---
title: "Adding metadata"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
    %\VignetteIndexEntry{Adding metadata}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r metadata, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup metadata, echo=FALSE}
library(rqti)
path <- fs::path_package("exercises", package = "rqti")
```

`r if(knitr::is_latex_output()) "# Adding metadata"`

Metadata---including details about creators, rights, and descriptions---is essential for ensuring accountability, legal compliance, and clarity in the management and use of assessment items and tests. This information helps track content origin and ownership, while also providing clear descriptions that facilitate better organization and retrieval of assessment resources.

We utilize ONYX's metadata implementation, which largely supports the IEEE Learning Object Metadata (LOM) standard. As a result, metadata is stored in XML format within the IMS manifest of the test data. However, it is important to note that this metadata may not be displayed by other learning management systems, and even Opal may overwrite it. The primary purpose is to maintain metadata within the original xml files being shared.

Here is an example of metadata with two contributors in the yaml section:

```{r comment='', echo = F}
cat(readLines(file.path(path, "metadata_template.Rmd")), sep = '\n')
```

Currently, the metadata may contain the following information:

- **description**: A string providing a description of the exercise content.
- **rights**: A string outlining the usage rights and terms associated with the exercise.
- **version**: A string indicating the version of the exercise.
- **contributor**: A list of contributor details, where each contributor entry may include the following information:
  - **name**: A string representing the contributor's name.
  - **role**: A string specifying the type of contribution. Possible values include: author, publisher, unknown, initiator, terminator, validator, editor, graphical designer, technical implementer, content provider, technical validator, educational validator, script writer, instructional designer, and subject matter expert. By default, `rqti` sets this value to "author".
  - **contribution_date**: A string representing the date of contribution. By default, `rqti` sets this to the current system date.
  
If you are working on a set of exercises, setting metadata for each one individually can be tedious. To streamline this process, you can use the environment variables `RQTI_AUTHOR` and `RQTI_RIGHTS`, which will automatically populate these fields with default values.

For example, you can create a `.Renviron` file and set the default author and usage rights as follows:

```{bash}
RQTI_AUTHOR="Ada Lovelace"
RQTI_RIGHTS="CC BY SA"
```

If you need to use non-default values, just specify the yaml attributes, which will override the environment variables.
