---
title: "Working with API OPAL from qti" 
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
    %\VignetteIndexEntry{api_opal}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

---
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
```{r setup, echo=FALSE}
library(qti)
```
## Introduction
`qti` package has functionality for uploading learning content to LMS OPAL for the following use-cases:

1. **Uploading a Zip Archive:**
If you already have a zip archive containing a test, you can use the `qti` package to upload it directly to LMS OPAL.

2. **Uploading an Rmd File:**
If you have an independent Rmd file with a task, the `qti` package can wrap it into a zip archive and deliver it to LMS OPAL.

3. **Uploading an XML File:**
If you have an independent XML file with a task, the `qti` package can wrap it into a zip archive and deliver it to LMS OPAL.

## Prerequisites
To use the OPAL API, the user must have specific privileges. Your username must allow you to log in to the system using a password, working with the api system through shibboleth authorization is not possible.

For authentication on OPAL `qti` works with two global environment variable: API_USER and API_PASSWORD. To set them, you need to call Sys.setenv(API_USER ='xxxxxxxxxxxxxxx') and Sys.setenv(API_PASSWORD ='xxxxxxxxxxxxxxx') or you can put these commands into .Rprofile.

```{r results="plaintext", comment=""}
Sys.setenv(API_USER ='__your_username__')
Sys.setenv(API_PASSWORD ='__your_password__')
```

Some universities use secure connection via Virtual Private Network. Before calling `upload2opal()` install, launch and log in VPN client of your university.
For TU Chemnitz [see here](https://www.tu-chemnitz.de/urz/network/access/vpn.html.en#client)

## Uploading test/task on OPAL
To do this just call `upload2opal()` with the file as a first parameter:
```{r results="plaintext", comment="", eval=FALSE}
file <- "my_zip_file.zip"
result <- upload2opal(file)
```
As a result you get:

1. A browser will open the OPAL page with test/task.
2. In R console there will be code '200' (this status code means that the request was successful).
3. Variable `result` will get a list with:
    - $key - this is an identifier of this resource on OPAL.
    - $display_name - this is a title of the resource on OPAL, it shows in browser.
    - $url - the permanent link on this resource.

`upload2opal()` always checks uniqueness of `display_name` in your personal repo of resources on OPAL. If some resources found, `qti` ask you what to do: rewrite, create new with the same `display_name`, or abort the uploading. By default `upload2opal()` uses file name as a `display_name`. But you can define your own as the second parameter:
```{r results="plaintext", comment="", eval=FALSE}
result <- upload2opal(file, "Exam WS")
```
## More Control

If you want to have more fine-grained control, consider all `upload2opal()` parameters:

### file

A length one character vector with path to file.

### display_name

Character string to entitle test/task on OPAL. Default is file name without extension.

### access

Integer that indicates access level:

- 1 - only the persons responsible for this learning resource.
- 2 - responsible and other authors.
- 3 - all registered users.
- 4 - public, default value.

### overwrite

Logical. If `TRUE`, it overwrites a resource in opal with the same `display_name`, in case there is only one resource with the specified `display_name.` Default is `TRUE.`

### endpoint

In case of not using "E-Learning-Informationsportal für Sächsische Hochschulen" you need to provide the url of your learning platform.

### open_in_browser

`TRUE` if you want to get your test/task opend after uploading immediately, `FALSE` for quiet uploading.

### api_user

If you need to try to upload under other credentials (not from the global environment).

### api_password

If you need to try to upload under other credentials (not from the global environment).

### cached

If `TRUE` (default) it keeps password in environment variable. Convenient for recurrent uploading during one session.

```{r results="plaintext", comment="", eval=FALSE}
# this is an example
file <- "my_zip_file.zip"
result <- upload2opal(file,
                      display_name = "Exam WS",
                      access = 1,
                      overwrite = FALSE,
                      open_in_browser = FALSE,
                      cached = FALSE)
```

## Error Handling

**403** - Authorization failed. You may need to run a VPN client

Some universities use secure connection via Virtual Private Network. To handle this install and login in VPN client of your university.
For TU Chemnitz [see here](https://www.tu-chemnitz.de/urz/network/access/vpn.html.en#client)

**401** Unauthorized

Your API_USER and/or API_PASSWORD are wrong or your credentials are not enough to work with API.
