---
title: "Compatibility with Learning Management Systems"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Compatibility with Learning Management Systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r compatibility, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup compatbility, echo=FALSE}
library(rqti)
```

`r if(knitr::is_latex_output()) "# Compatibility with Learning Management Systems"`

The files generated by the `rqti` package are fully compatible with the OPAL LMS. Furthermore, adhering to QTI 2.1 specifications, these files are suitable for use in any LMS supporting QTI 2.1. You can find a list of QTI-compatible LMS platforms here: <https://en.wikipedia.org/wiki/QTI>.

To upload your tasks to an LMS, create a zip archive containing the test and import it into the target LMS.

We have conducted compatibility tests by uploading `rqti` zip archives to LMS platforms such as OpenOlat and Canvas. In most instances, tasks generated by `rqti` behaved as expected within these LMS platforms. However, we have identified some inconsistencies, documented below. Since our files are QTI 2.1 compatible (with verification and automated tests for all task types), issues typically arise from the LMS side.

If you use a different LMS and encounter problems, please open an issue on GitHub: https://github.com/shevandrin/rqti/issues

## OpenOlat

The following functionalities are currently non-functional on OpenOlat:

- The parameters `include_lower_bound` and `include_upper_bound` in the tolerance customization of numeric gaps are ignored. This is a minor problem since it is usually irrelevant whether the bounds are included or not. Still, we are actively investigating this issue.
<!-- - The parameter `data_allow_paste` in essays currently does not work because it is implemented differently to OPAL. This will be fixed soon. Note that this attribute is not compatible with QTI 2.1. -->

<!-- - Test upload is not operational due to OpenOlat utilizing a custom test structure that is not entirely compatible with QTI. Uploading a QTI test will extract individual tasks, displaying them in Olat, but the overall test disappears. This also happens with the official IMS QTI examples. In the future we will provide a custom class to handle this. -->

## Canvas

Note that Canvas exports to the fairly old QTI 1.2 version, which makes it difficult to understand what is happening internally and to diagnose or resolve these issues.

The following functionalities encounter problems when used with Canvas:

* The `inlineChoice` task type does not appear to be supported.
* Feedback information seems to be ignored during import.
<!-- - Feedback messages intended to be displayed regardless of answer correctness (modal feedback), do not appear.  -->
<!-- - All feedback types for the `essay` task type are non-functional. -->
* `textEntryInteraction` elements are incorrectly imported as essay questions, rendering both numeric and text gap items non-functional.
<!-- - Customization of tolerance for numeric gaps does not work. -->
* Handling of text input length and placeholders is not supported.
  <!-- todo: for essay? -->
* Tables are converted to either `match` or `categorization` interactions, which leads to several issues:
  * One-in-row tables lose distractors (i.e., options that are not mapped to any row); one-in-column tables have not yet been tested. Directed pairs work correctly; MPC tables have not yet been tested.

<!-- todo: directedpairs work just fine, which makes sense because source and target are completely used, no distractors; multiplechoice table has to be checked still; what i do not quite get is when categorization (dragging) is used and when matching is used? format seems to be the same, namely one-in-row table...-->

<!-- - rendering only tables with a single possible answer in each row meaningful (one-in-row-table). -->

<!-- - The `order` task type is not supported. This is now possible 2026-03-17-->
## Test files

Official conformance test files for QTI v2.1:

https://www.imsglobal.org/developers/apipalliance/conformance/QTIconformanceresources.cfm

These resources are incomplete. In particular, they do not include `textEntryInteraction` items with a `responseDeclaration` of `baseType="float"` (i.e., numeric gap questions), and only a single variant of `matchInteraction` is provided. Several other interaction types are also missing.

Additional examples can be obtained from the implementation guide:

https://www.imsglobal.org/question/qtiv2p1/imsqti_implv2p1.html
