---
title: "Compatibility with Learning Management Systems"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Compatibility with Learning Management Systems}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r compatibility, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup compatbility, echo=FALSE}
library(rqti)
```

`r if(knitr::is_latex_output()) "# Compatibility with Learning Management Systems"`

The files generated by the `rqti` package are fully compatible with the OPAL LMS. Furthermore, adhering to QTI 2.1 specifications, these files are suitable for use in any LMS supporting QTI 2.1. You can find a list of QTI-compatible LMS platforms here: <https://en.wikipedia.org/wiki/QTI>.

To upload your tasks to an LMS, create a zip archive containing the test and import it into the target LMS.

We have conducted compatibility tests by uploading `rqti` zip archives to LMS platforms such as OpenOlat and Canvas. In most instances, tasks generated by `rqti` behaved as expected within these LMS platforms. However, we have identified some inconsistencies, documented below. Since our files are QTI 2.1 compatible (with verification and automated tests for all task types), issues typically arise from the LMS side.

If you use a different LMS and encounter problems, please open an issue on GitHub: https://github.com/shevandrin/rqti/issues

## OPAL

As noted above, our files are fully compatible with OPAL, and we even support selected QTI 2.2 features.

In particular, downloadable files and calculator support are available in OPAL, but only in connection with QTI 2.2.

### Extra `assessmentTest` Attributes

Concretely, this functionality is currently based on custom attributes in the `assessmentTest` element:

```xml
<assessmentTest
  ...
  data-downloads="file://downloads/;"
  data-features="scientific-calculator;mark-items;show-test-time;">
```

Under QTI 2.2, this is permissible, although it should be clearly documented.

A simpler alternative would be to include such files directly in the content package, for example through a dedicated `downloads` folder referenced in the manifest. However, this raises an important issue in exam settings, where file downloads may be restricted, for example by Safe Exam Browser. In such cases, files should be managed explicitly as downloadable LMS resources rather than being encoded in the test definition itself. This would be possible without relying on custom `data-` attributes.

More generally, we believe such attributes should be avoided whenever possible, because they weaken the idea of a common standard.

With regard to the calculator, this may be better understood as a feature of the LMS rather than of the test itself. Accordingly, it could be configured at the LMS or test-delivery level rather than within the QTI test definition. The same consideration applies to other `data-features` such as `mark-items` and `show-test-time`. More broadly, the additional flexibility introduced in QTI 2.2 is not necessarily problematic; it may also indicate where the standard itself still lacks useful features.

### Tolerance for Text Gaps

Tolerance handling for text-entry questions is currently implemented via extra tags, that are not compatible with QTI. In this case, however, we do see a legitimate need for extending the QTI standard, because tolerance is an important feature for text-response processing and is not adequately supported by the base specification.

Example:

```xml
<setOutcomeValue identifier="SCORE_codieren">
  <mapTolResponse xmlns="http://bps-system.de/xsd/imsqti_ext_maptolresponse"
                  identifier="codieren"
                  tolerance="2"
                  toleranceMode="absolute"/>
</setOutcomeValue>
```

### Allow Pasting in Essay Questions

The attribute `data-allowPaste` in `extendedTextInteraction` is fine in QTI 2.2. However, this functionality can usually be handled at the system level, for example through Safe Exam Browser, and therefore does not need to be encoded in the QTI test definition itself.

### MathML

A custom namespace prefix for MathML is ignored. For example, the following does not work:

### Referencing files

You cannot reference files or images (e.g. via `<a href=...>`). They must be embedded directly in the file via base64 encoding.

```xml
xmlns:m="http://www.w3.org/1998/Math/MathML"
...
<m:math>
  ...
</m:math>
```

By contrast, using the MathML namespace directly on the `math` element works:

```xml
<math xmlns="http://www.w3.org/1998/Math/MathML">
  ...
</math>
```

## OpenOlat

For OpenOlat, a dedicated class AssessmentTestOpenOlat is available.
Compared to the standard AssessmentTest, it allows specifying OpenOlat-specific settings (e.g., navigation behavior, visibility of elements, number of attempts).

When creating a test via createQtiTest(), the corresponding configuration file (QTI21PackageConfig.xml) is automatically generated and included in the package.

The following functionalities are currently non-functional on OpenOlat:

- The parameters `include_lower_bound` and `include_upper_bound` in the tolerance customization of numeric gaps are ignored. This is a minor problem since it is usually irrelevant whether the bounds are included or not. Still, we are actively investigating this issue.
<!-- - mathjax does not work properly -->
<!-- - allowPaste is same as for OPAL -->
<!-- - The parameter `data_allow_paste` in essays currently does not work because it is implemented differently to OPAL. This will be fixed soon. Note that this attribute is not compatible with QTI 2.1. -->

<!-- - Test upload is not operational due to OpenOlat utilizing a custom test structure that is not entirely compatible with QTI. Uploading a QTI test will extract individual tasks, displaying them in Olat, but the overall test disappears. This also happens with the official IMS QTI examples. In the future we will provide a custom class to handle this. -->

## Canvas

Note that Canvas exports to the fairly old QTI 1.2 version, which makes it difficult to understand what is happening internally and to diagnose or resolve these issues.

Canvas is transitioning to a new quizzes interface, so maybe this one will work better.

The following functionalities encounter problems when used with Canvas:

* Sometimes items are imported without error message but are not displayed.
* The `inlineChoice` task type does not appear to be supported.
* Feedback information seems to be ignored during import.
<!-- - Feedback messages intended to be displayed regardless of answer correctness (modal feedback), do not appear.  -->
<!-- - All feedback types for the `essay` task type are non-functional. -->
* `textEntryInteraction` elements are incorrectly imported as essay questions, rendering both numeric and text gap items non-functional.
<!-- - Customization of tolerance for numeric gaps does not work. -->
* Handling of text input length and placeholders is not supported.
  <!-- todo: for essay? -->
* Tables are converted to either `match` or `categorization` interactions, which leads to several issues:
  * One-in-row tables lose distractors (i.e., options that are not mapped to any row); one-in-column tables have not yet been tested. Directed pairs work correctly (since there are no distractors); MPC tables have not yet been tested.

<!-- todo: directedpairs work just fine, which makes sense because source and target are completely used, no distractors; multiplechoice table has to be checked still; what i do not quite get is when categorization (dragging) is used and when matching is used? format seems to be the same, namely one-in-row table...-->

<!-- - rendering only tables with a single possible answer in each row meaningful (one-in-row-table). -->

<!-- - The `order` task type is not supported. This is now possible 2026-03-17-->

## ILIAS

ILIAS does not explicitly state which version of QTI it supports. However, it seems to rely on QTI 1.2.

As a consequence, files generated with modern tools targeting QTI 2.1 (such as *rqti*) are not compatible with ILIAS. Given that QTI 1.x is deprecated and no longer aligns with current specifications, we do not plan to support it going forward.

## Blackboard

Blackboard supports QTI 2.1, but with a significant limitation:

> “Questions using the optional QTI response processing are skipped and not imported.” (https://help.anthology.com/blackboard/instructor/en/assessments/questions/reuse-questions/qti-packages.html)

In practice, this restriction is critical. QTI response processing defines how answers are evaluated and scored. If such questions are omitted during import, essential parts of the assessment logic are lost.

From our perspective, importing questions without their associated response processing undermines the integrity of the assessment. Consequently, this limitation substantially reduces the usefulness of QTI 2.1 imports in Blackboard.

## Test files

Official conformance test files for QTI v2.1:

https://www.imsglobal.org/developers/apipalliance/conformance/QTIconformanceresources.cfm

These resources are incomplete. In particular, they do not include `textEntryInteraction` items with a `responseDeclaration` of `baseType="float"` (i.e., numeric gap questions), and only a single variant of `matchInteraction` is provided. Several other interaction types are also missing.

Additional examples can be obtained from the implementation guide:

https://www.imsglobal.org/question/qtiv2p1/imsqti_implv2p1.html

## APIs

OPAL provides a strong API that supports direct upload of QTI files.

OpenOlat also offers an API, but it is currently unclear whether QTI files can be uploaded directly. The API documentation can be accessed at http://localhost:8080/restapi/api-docs/ for a local installation, although a server URL can of course be used as well. Potentially relevant endpoints include `/repo/entries` (`PUT`) and `/qpool/items` (`POST`, `PUT`). However, we have not yet tested these endpoints.

Blackboard provides an API as well: https://developer.blackboard.com/portal/displayApi. At present, it is unclear whether this API supports QTI upload, and we have not yet tested it. Based on the available documentation, this currently seems unlikely.

Canvas provides an API that appears to support both uploading and migrating QTI files, although we have not yet tested this functionality: https://mitt.uib.no/doc/api/all_resources.html, see endpoint `/api/v1/accounts/:account_id/content_migrations`. Also see: https://community.instructure.com/en/kb/articles/658474-classic-quizzes-vs-new-quizzes-feature-comparison and https://developerdocs.instructure.com/services/new-quizzes/public/api-endpoints/new_quizzes as well as https://community.instructure.com/en/kb/articles/661050-how-do-i-import-a-quiz-from-a-qti-package-in-new-quizzes.
