---
title: "Compatibility"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Compatibility}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r, echo=FALSE}
library(rqti)
```

## Compatibility with Learning Management Systems (LMS)

The outcomes generated by the `rqti` package are fully compatible with the LMS Opal. Additionally, according to QTI 2.1 specifications, these outcomes can be utilized in any LMS that supports them. A list of LMS platforms compatible with QTI can be found here <https://en.wikipedia.org/wiki/QTI>.

To upload your tasks to an LMS, you can create a zip archive containing the test and then import it into the target LMS.

We have conducted compatibility tests by uploading `rqti`-zip archives to LMS platforms such as OpenOlat and Canvas. In most cases, the tasks generated by `rqti` exhibited the expected behavior within these LMS platforms. However, we have identified some inconsistencies, which are documented below.

## OpenOlat

Here is the list of functionality that does not work on OpenOlat:
- parameters `include_lower_bound` and `include_upper_bound` in tolerance customization of NumericGap.


## Canvas

Here is the list of functionality that does not work on Canvas:

- Order type of the task.
- Feedback messages that should be shown, regardless of whether the answer was correct or incorrect (ModalFeedback).
- All types of Feedback for Essay type of the task.
- Tolerance customization for NumericGap.
- Managing size of the text inputs and placeholders.
- All tables are converted to 'match' type, so only table with one possible answer in each row is meaningful.



