---
title: "Integration of the exams Package in rqti"
output: rmarkdown::html_vignette
date: "`r Sys.Date()`"
vignette: >
    %\VignetteIndexEntry{Integration of the exams Package in rqti}
    %\VignetteEngine{knitr::rmarkdown}
    %\VignetteEncoding{UTF-8}
---

```{r setup exams, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>"
)
source("helper.R")
```

```{r setup2 exams, echo=FALSE}
library(rqti)
```

`r if(knitr::is_latex_output()) "# Integration of the exams Package in rqti"`

## Using exams Rmd files in section()

In addition to native `rqti` task definitions, the `rqti` package allows the use of tasks written in the format of the `exams` package.

This integration makes it possible to reuse existing `exams` R Markdown files and include them directly in `rqti` workflows.  
When an `.Rmd` file is provided, `rqti` automatically detects its format based on the structure of the file. Based on this detection, the file is processed accordingly.

R Markdown files from the `exams` package can be passed directly to the `section()` function, just like native `rqti` tasks and/or objects.

```{r sectionWithExams, eval = F}
sect <- section(
        content = c(
            "rqti_task.Rmd",      # native rqti format
            "exams_task.Rmd",     # exams format
            sc_object            # existing rqti object
        )
)
```

rqti converts exams_task.Rmd into an XML file in QTI 2.1 format using functionality from the exams package.

## Integration with OpenOLAT configuration

The rqti package also relies on functionality from the exams package to create configuration files required by learning management systems such as OpenOLAT.

In particular, the configuration file (QTI21PackageConfig.xml) is generated using helper functions from exams.
This ensures compatibility with OpenOLAT while keeping the implementation aligned with existing tools.
